---
title: "IMPAcTB Day 14 testing data and stats"
author: "Pablo Maldonado"
date: "6/8/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r global options}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, message = FALSE, warning = FALSE)

```

## Loading packages

```{r message=FALSE, warning=FALSE, include=FALSE}
library(jtools)
library(readxl)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(tidyverse)
library(scales)
library(stringr)
library(tidyr)
library(knitr)
library(forcats)
library(broom)
library(ggfortify)
library(stats)
library(ggpubr)
library(grDevices)
library(rstatix)
library(writexl)
library(purrr)
library(kableExtra)
library(ggbeeswarm)
library(multcomp)
library(DescTools)
library(car)
library(exactRankTests)
library(readr)
library(ggeffects)
library(GGally)
library(gridExtra)
library(emmeans)
library(viridis)
library(vcd)
library(ggmosaic)
#mm7qNhXs8FN4CFS

citation("ggeffects")
packageVersion("ggeffects")

citation("tidyr")
packageVersion("ggplot2")
```

MULTI CSV SHEETS MALE FEMALE
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Read in all CSV files
files <- list.files(path = "/Volumes/rstor-henao_lab/Pablo/IMPAcTB-Flow-pipeline/Base_period_Treg", pattern = "*.csv", full.names = TRUE)

dfs <- lapply(files, function(file) {
  # Read the CSV file and clean up column names
  df <- read_csv(file)
    df <- df %>%
    rename("Sample" = colnames(.)[1]) %>%
    dplyr::select(Sample, contains("Count")) %>%
    rename_all(funs(str_replace(., "\\|.+", ""))) %>%
    rename_all(~ str_remove(., "Leukocytes/Single Cells/")) %>%
    rename_all(~ str_remove(., "Leukocytes/")) %>%
    rename_all(~ str_remove(., "LIVE/")) %>%
    # mutate(Sample = str_replace_all(Sample, "\\b[A-Za-z][0-9]+\\b", "")) %>%
    rename_all(funs(str_replace_all(., ",", ""))) %>%
    rename_all(funs(str_replace_all(., "/", " "))) %>%
    rename_all(funs(str_replace_all(., "\\\\", " ")))  %>%
    rename_all(~ stringr::str_replace_all(., "Q\\d+\\:", "")) %>%
    rename("cells in sample" := matches("Count")) %>%
    rename("leukocytes" := matches("Leukocytes")) %>%
    rename("live leukocytes" := matches("LIVE")) %>%
    rename("single cells" := matches("Single Cells")) %>%
  # Removing logical vectors, not sure why its adding these
  dplyr::select(where(~ !any(is.logical(.)) | is.numeric(.))) %>%
  # Remove last two rows of SD and Mean
  slice(1:(n() - 2))
  # Extract the sex from the file name
  sex <- ifelse(grepl("female", file), "female", "male")
  df <- df %>% mutate(sex = sex)
  # Move the sex column to the second position
  df <- df %>% relocate(sex, .after = 1)
  # Extract the day from the file name
  day <- str_extract(file, "(?<=Day\\s)\\d+")
  df <- df %>% mutate(day = as.character(day))
  # Move the day column to the third position
  df <- df %>% relocate(day, .after = 2)
  
  return(df)
})

# Combine all data frames into one dataframe
Df1 <- bind_rows(dfs)
Df1

#str(dfs)
#tail(Df1)

# Check for NA values in Df1
#na_counts <- colSums(is.na(Df1))

# Print the column names with NA counts
#print(na_counts)
Df1

# barbering, fighting, UD, injury, new cage, euthanize, illness
```

## MAKING DATA TIDY
```{r echo=TRUE, message=FALSE, warning=FALSE}
#tidy_Df1 <- pivot_longer(data = Df1, cols =  starts_with("CD3"), names_to = "cell_types", values_to = "cell type count")

tidy_Df1 <- pivot_longer(data = Df1, 
                          cols = starts_with("CD3") | starts_with("live") | starts_with(" NK1.1"), 
                          names_to = "cell_types", 
                          values_to = "cell type count")

tidy_Df1 <- tidy_Df1 %>%
  separate(col = "Sample", into = c("group", "mouse_ID"), sep = "_") %>%
  mutate(mouse_ID = str_replace(mouse_ID, ".fcs", ""))

# Trim extra spaces
tidy_Df1$cell_types <- str_replace_all(tidy_Df1$cell_types, "\\s+", " ")
tidy_Df1$cell_types <- str_trim(tidy_Df1$cell_types)
tidy_Df1$group <- trimws(tidy_Df1$group)

# Fix Group Column
tidy_Df1 <- tidy_Df1 %>%
  mutate(group = gsub("^[A-Za-z]\\d{1,2}\\s", "", group))
tidy_Df1$group <- str_replace_all(tidy_Df1$group, "-", " ")


tidy_Df1 
```

## Insert trials and successes (cell counts and parent populations)
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Filter CD3+ CD4+, CD3+ CD4+ CD62L- CD44+ to find trials and successes
# tidy_Df1$cell_types [3]

###
t_cell_activation <- tidy_Df1 %>%
  dplyr::filter(cell_types == "live leukocytes" | cell_types == "CD3- CD19+") 

t_cell_activation <- t_cell_activation %>%
  pivot_wider(names_from = cell_types, values_from = `cell type count`) %>%
  rename(trials = "live leukocytes", successes = "CD3- CD19+") %>%
  mutate(failures = trials - successes) %>%
  dplyr::select(-`cells in sample`, -leukocytes, -`single cells`)



# Recode the condition and group names
t_cell_activation$group <- factor(t_cell_activation$group, levels = c("Saline", "BCG", "ID93", "BCG+ID93"))

t_cell_activation <- t_cell_activation %>%
  mutate(group = ifelse(group == "ID93", "ID93-GLA-SE",
                       ifelse(group == "BCG+ID93", "BCG+ID93-GLA-SE",
                              ifelse(group == "Saline", "Saline",
                                     ifelse(group == "BCG", "BCG", group)))))



t_cell_activationPLOT <- t_cell_activation %>%
  mutate(proportion_of_activated_tcells = (successes/trials*100)) 
t_cell_activationHIST <- t_cell_activation
t_cell_activationF1_Score <- t_cell_activation %>%
  mutate(proportion_of_activated_tcells = (successes/trials)) 

t_cell_activation
```


# Set reference group
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Convert 'result' into a factor data type.
t_cell_activation$successes <- as.numeric(t_cell_activation$successes)
# Convert 'group' into a factor data type.
t_cell_activation$group <- factor(t_cell_activation$group)
# Convert 'day' into a factor data type.
t_cell_activation$day <- as.factor(t_cell_activation$day)
t_cell_activation$failures <- as.numeric(t_cell_activation$failures)
t_cell_activation$sex <- as.factor(t_cell_activation$sex)

# Reorder groups for visuals
t_cell_activation <- t_cell_activation %>%
  mutate(group = fct_relevel(group, "Saline", "BCG", "ID93-GLA-SE", "BCG+ID93-GLA-SE")) #%>%
  #mutate(day = ifelse(day == 1, -1, day))
  
t_cell_activation$group <- relevel(t_cell_activation$group, ref = "Saline")
```



Distribution of cell phenotype per mouse and checking for normality

```{r}
# # Convert successes to numeric (if it's not already numeric)
#t_cell_activationHIST$successes <- as.numeric(t_cell_activationHIST$successes)

# Reorder groups for visuals
t_cell_activationHIST <- t_cell_activationHIST %>%
  mutate(group = fct_relevel(group, "Saline", "BCG", "ID93-GLA-SE", "BCG+ID93-GLA-SE"))
t_cell_activationHIST$group <- relevel(t_cell_activationHIST$group, ref = "Saline")

summary(t_cell_activationHIST)

capitalize_labels <- function(variable) {
  return(paste0(toupper(substring(variable, 1, 1)), substring(variable, 2)))
}


ggplot(data = t_cell_activationHIST) +
  geom_mosaic(aes(x = product(sex), fill = group), divider = ddecker()) +
  facet_grid(. ~ day, scales = "free_y", labeller = labeller(sex = capitalize_labels)) +
  scale_fill_viridis_d(name = "Vaccine") +
  labs(x = "", y = "") +
  theme_bw() +
    theme(
    strip.text = element_text(color = "black", size = 1.1 * rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
    axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
    axis.title.y = element_text(color = "black", size = 1.3 * rel(1)),
    legend.position = "none") +
  geom_mosaic_text(aes(x = product(sex), fill = group, label = after_stat(.wt)), 
                   color = 'black', 
                   fill = 'white', 
                   repel = TRUE, 
                   as.label = TRUE)

subset(t_cell_activationHIST, sex == "male" & group == "Saline")
subset(t_cell_activationHIST, group == "BCG")

shapiro.test(t_cell_activationHIST$successes)

# Check normality of groups
shapiro_results <- tapply(t_cell_activationHIST$successes, t_cell_activationHIST$group, shapiro.test)
# Check normality of groups + sex
shapiro_results_by_sex <- tapply(t_cell_activationHIST$successes, 
                          interaction(t_cell_activationHIST$group, t_cell_activationHIST$sex), 
                          shapiro.test)
# Print the results
shapiro_results
shapiro_results_by_sex

subset(t_cell_activationHIST, sex == "male")
subset(t_cell_activationHIST, sex == "female")
```


```{r}
# ggplot(t_cell_activationHIST, aes(x = successes, fill = group)) +
#   geom_histogram(binwidth = 500, color = "black") +
#   scale_fill_viridis_d(name = "Vaccine") +  # Add legend title
#   labs(y = "Frequency", x = "Activated T Cells") +  
#   theme_minimal() +
#     theme(
#     strip.text = element_text(color = "black", size = 1.1 * rel(1)),
#     axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
#     axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
#     axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
#     axis.title.y = element_text(color = "black", size = 1.3 * rel(1)),
#     legend.text = element_text(color = "black", size = 11),
#     legend.title = element_text(color = "black", size = 11)) 

ggplot(t_cell_activationHIST, aes(x = successes, fill = "bar")) +
  geom_histogram(binwidth = 500, color = "black", fill = "grey") +
  labs(y = "Frequency", x = "CD8+ T Cells") +  
  theme_minimal() +
  theme(
    strip.text = element_text(color = "black", size = 1.1 * rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
    axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
    axis.title.y = element_text(color = "black", size = 1.3 * rel(1)),
    legend.position = "none")


ggplot(t_cell_activationHIST, aes(x = successes, fill = group)) +
  geom_histogram(binwidth = 750, color = "black") +
  scale_fill_viridis_d(name = "Vaccine") +  # Add legend title
  labs(y = "Frequency", x = "CD8+ Distribution Across Groups") +  
  facet_wrap(~ group) +# Add Y-axis title
  theme_minimal() +
  theme(
    strip.text = element_text(color = "black", size = 1.1 * rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
    axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
    axis.title.y = element_text(color = "black", size = 1.3 * rel(1)),
    legend.position = "none")
```


# Plot actual CD4+ CD44+ populations for comparison to predicited outcomes
```{r}
Treg_activationPLOT <- t_cell_activationPLOT  %>%
  mutate(group = fct_relevel(group, "Saline", "BCG", "ID93-GLA-SE", "BCG+ID93-GLA-SE")) %>%
  ggplot(aes(x = day, y = proportion_of_activated_tcells, fill = group, color = group)) +
  geom_boxplot(width = 0.5, alpha = 0.7, position = position_dodge(width = 0.75)) +
  geom_point(size = 3, shape = 21, alpha = 0.9, na.rm = TRUE, color = "black",
             position = position_dodge(width = 0.75)) +
    scale_color_viridis_d(name = "Vaccine", alpha = 1) +  
  scale_fill_viridis_d(name = "Vaccine", alpha = 1) +  
  # scale_fill_manual(values = c(alpha("red3", 0.7), alpha("darkolivegreen3", 0.7), alpha("seagreen", 0.7), alpha("steelblue1", 0.7))) +
  # scale_color_manual(values = c(alpha("red3", 0.7), alpha("darkolivegreen3", 0.7), alpha("seagreen", 0.7), alpha("steelblue1", 0.7))) +
  facet_grid(. ~ sex, scales = "free_y", labeller = labeller(sex = capitalize_labels)) +
  labs(title = "Observed CD8+", x = "Days Post Infection", y = "Percentage of Live", color = "Vaccine") +
  #guides(fill = "none", shape = guide_legend(title = "Vaccine")) +
  theme_bw() + 
  theme(
    strip.text = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
    axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
    axis.title.y = element_text(color = "black", size = 1.4 * rel(1)),
    legend.position = "bottom",
    legend.title = element_text(color = "black", size = 1.3 * rel(1)),
    legend.text = element_text(color = "black", size = .9 * rel(1)),
    plot.title = element_text(color = "black", size = 15))

Treg_activationPLOT

# #save to pdf
# pdf(file = "/Volumes/rstor-henao_lab/Pablo/IMPAcTB-Flow-pipeline/Treg_activationPLOT.pdf",   # The directory you want to save the file in
#    width = 10, # The width of the plot in inches
#    height = 5) # The height of the plot in inches
# print(Treg_activationPLOT)
# dev.off()
```



$$
log(1−pp)=β0+β1χ1+β2χ2+β3χ3+β4χ4+β5χ5+β6χ6+β7(χ1χ4)+β8(χ2χ4)+β9(χ3χ4)+β10(χ1χ5)+β11(χ2χ5)+β12(χ3χ5)+β13(χ1χ6)+β14(χ2χ6)+β15(χ3χ6)+β16(χ4χ6)+β17(χ5χ6)+β18(χ1χ4χ6)+β19(χ2χ4χ6)+β20(χ3χ4χ6)+β21(χ1χ5χ6)+β22(χ2χ5χ6)+β23(χ3χ5χ6)
$$

## GLM modeling for: group * day + sex | group * day * sex | group * day
```{r echo=TRUE}

l_mod2 <- glm(cbind(successes, failures) ~ group * day + sex, 
              family = quasibinomial(link = "logit"), data = t_cell_activation)
summary(l_mod2)
# accounting for sex


l_mod1 <- glm(cbind(successes, failures) ~ group * day * sex,
              family = quasibinomial(link = "logit"), data = t_cell_activation)
summary(l_mod1)

# l_mod11 <- glm(cbind(successes, failures) ~ group * day * sex,
#               family = binomial(link = "logit"), data = t_cell_activation)
# summary(l_mod11)
```
```{r}
# Extract coefficients, standard errors, p-values, and significance levels
coefficients <- coef(summary(l_mod1))
coefficients <- as.data.frame(coefficients)

# Rename columns
colnames(coefficients) <- c("Estimate", "Std.Error", "t.value", "Pr(>|t|)") 

coefficients %>% 
    rownames_to_column('Predicting Variable')

# Add significance level column
coefficients$Significance <- ifelse(coefficients$`Pr(>|t|)` < 0.001, "***",
                             ifelse(coefficients$`Pr(>|t|)` < 0.01, "**",
                             ifelse(coefficients$`Pr(>|t|)` < 0.05, "*",
                             ifelse(coefficients$`Pr(>|t|)` < 0.1, ".", ""))))

coefficients <- coefficients %>% 
    rownames_to_column('Predicting Variable')

# Print the dataframe
print(coefficients)
```

```{r}
#plot coefficients
coefficients <- summary(l_mod1)$coefficients[, c("Estimate", "Std. Error")]

# Create a data frame
coefficients_df <- data.frame(
  Variable = rownames(coefficients),
  Estimate = coefficients[, "Estimate"],
  SE = coefficients[, "Std. Error"]
)
# Assuming your dataframe is called coefficients_df
coefficients_df$Variable <- gsub("group", "", coefficients_df$Variable)
coefficients_df$Variable <- gsub("sex", "", coefficients_df$Variable)
coefficients_df$Variable <- gsub("male", "Male", coefficients_df$Variable)
coefficients_df$Variable <- gsub("day", "Day", coefficients_df$Variable)
coefficients_df$Variable <- gsub(":", " & ", coefficients_df$Variable)

# plot it
CoefficientsandConfidence_Intervals_Treg <- ggplot(coefficients_df, aes(x = reorder(Variable, Estimate), y = Estimate, ymin = Estimate - 1.96 * SE, ymax = Estimate + 1.96 * SE)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  coord_flip() +
  labs(title = "CD8+ Estimated Effects",
       x = "Variable",
       y = "Estimated Coefficient") +
  theme_bw() +
    theme(
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
    axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
    axis.title.y = element_text(color = "black", size = 1.4 * rel(1)),
    plot.title = element_text(color = "black", size = 15))

CoefficientsandConfidence_Intervals_Treg

# pdf(file = "/Volumes/rstor-henao_lab/Pablo/IMPAcTB-Flow-pipeline/CoefficientsandConfidence_Intervals_Treg.pdf",   # The directory you want to save the file in
#     width = 8, # The width of the plot in inches
#     height = 5) # The height of the plot in inches
# print(CoefficientsandConfidence_Intervals_Treg)
# dev.off()
```

## Model diagnostics 

# Drop-in-deviance test to compare models
# The Likelihood Ratio Test compares the fit of two nested models by examining the difference in their log-likelihoods or deviances. It is commonly used to assess the significance of adding or removing predictor variables from a model
```{r echo=TRUE}
# Perform Likelihood Ratio Test
drop_in_dev1 <- anova(l_mod2, l_mod1, test = "Chisq")

drop_in_dev1

```

# This summary outlines the calculation and interpretation of the ratio of deviance explained by a GLM model (l_mod1) to the null deviance:
calculate the ratio of deviance explained by the model to the null deviance.
The ratio is calculated by dividing the deviance explained by the model by the null deviance.
The null deviance represents the deviance when no predictors are included in the model, essentially fitting a model with only an intercept.
The deviance of the model is the difference between the null deviance and the deviance after fitting the model.
This ratio provides insight into the proportion of deviance explained by the predictors included in the model relative to the total deviance in the null model, ranging from 0 to 1.
A higher ratio indicates that a larger proportion of the deviance is explained by the predictors in the model.

```{r}
1- (l_mod1$deviance/l_mod1$null.deviance)
1- (l_mod2$deviance/l_mod2$null.deviance)
```
# To determine the better model, we compare the ratios of deviance explained by each model. In this case, l_mod1 has a higher ratio (approximately 56.63%) compared to l_mod2 (approximately 42.51%), indicating that l_mod1 is the better model.
In summary, l_mod1 is considered the better model based on the ratios of deviance explained relative to the null deviance


# Residual Plots
```{r echo=TRUE}
# Create a residual vs fitted plot
residuals <- residuals(l_mod1)

dev_res <- residuals(l_mod1, type = "deviance")
fitted_values <- fitted(l_mod1)

# Create the residuals vs. fitted plot
plot(fitted_values, dev_res, main = "CD8+ Residuals vs. Fitted", 
     xlab = "Fitted Values", ylab = "Residuals")

# Add a horizontal reference line at y = 0 (optional)
abline(h = 0, col = "red", lty = 2)

# Create a QQ plot of deviance residuals
qqnorm(residuals)
qqline(residuals)

```

## GLM modeling and plotting expected outcomes of group * day + sex
```{r echo=TRUE}
#Plot and interpret effects
# plotGroup <- effect_plot(l_mod1, pred = group, interval = TRUE, y.label = "Probability of Activated T-cells")
# plotSex <- effect_plot(l_mod1, pred = sex, interval = TRUE, y.label = "Probability of Activated T-cells")
# plotDay <- effect_plot(l_mod1, pred = day, interval = TRUE, y.label = "Probability of Activated T-cells")
# 
# grid.arrange(plotGroup, plotSex, plotDay, ncol = 3)
# 
# 
# 
# t_cell_activation
# Calculate the probabilities for all combinations using testMod

combinations <- expand.grid(sex = levels(t_cell_activation$sex),
                            day = levels(t_cell_activation$day),
                            group = levels(t_cell_activation$group))

results <- combinations %>%
  rowwise() %>%
  mutate(probability = (round(100 * predict(l_mod1, newdata = data.frame(sex, day, group), type = "response"))))

# Create a heatmap
Treg_probability_heatmap <- ggplot(results, aes(x = day, y = group)) +
  geom_tile(aes(fill = probability)) +
  facet_grid(. ~ sex, scales = "free_y", labeller = labeller(sex = capitalize_labels)) +
  scale_fill_viridis_c(name = "Probability", labels = function(x) paste0(x, "%")) +# Add 5 to each label
  theme_minimal() +
  labs(title = "Probability of CD8+", x = "Day", y = " ", fill = "Probability of Activated T-cells") +
  theme(
    strip.text = element_text(color = "black", size = 1.1 * rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
    axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
    axis.title.y = element_text(color = "black", size = 1.3 * rel(1)),
    legend.text = element_text(color = "black", size = 11),
    legend.title = element_text(color = "black", size = 11),
        plot.title = element_text(color = "black", size = 15))# Adjust the font size as needed


Treg_probability_heatmap

# pdf(file = "/Volumes/rstor-henao_lab/Pablo/IMPAcTB-Flow-pipeline/Treg_probability_heatmap.pdf",   # The directory you want to save the file in
#     width = 8, # The width of the plot in inches
#     height = 5) # The height of the plot in inches
# print(Treg_probability_heatmap)
# dev.off()


```



# Predicted probabilities for all variables
```{r}

# Define custom colors with reduced opacity
#custom_colors <- c(alpha("red3", 0.7), alpha("darkolivegreen3", 0.7), alpha("seagreen", 0.7), alpha("steelblue1", 0.7))
  #scale_fill_manual(values = custom_colors) +
  #scale_color_manual(values = custom_colors) +

# Generate predictions
predictor_terms <- c("day", "group", "sex")
predictions <- ggpredict(l_mod1, terms = predictor_terms)
#predictions1 <- ggemmeans(l_mod2, terms = predictor_terms)

#predict(l_mod1, type = "response")
#predictions


plot(predictions) +
  scale_color_viridis_d(name = "Vaccine") +  
  scale_fill_viridis_d(name = "Vaccine") +  
  geom_point(position = position_jitterdodge(), size = 3, alpha = 0.7, width = 0.3) +
  theme_bw()


Treg_predictions <- ggplot(predictions, aes(x = x, y = predicted, group = group, color = group, fill = group)) +
  geom_point(position = position_dodge(width = 0.3), size = 3, alpha = .9) +
  geom_line(aes(group = group), size = .5, alpha = 1) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, position = position_dodge(width = 0.3)) +
  scale_color_viridis_d(name = "Vaccine", alpha = 1) +  
  scale_fill_viridis_d(name = "Vaccine", alpha = 1) +  
  labs(title = "Predicted CD8+", x = "Day", y = "Probability", fill = "Vaccine", color = "Vaccine") +
  facet_grid(. ~ facet, scales = "free_y", labeller = labeller(facet = capitalize_labels)) +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, breaks = seq(0, .25, by = 0.05), limits = c(0, .25)) +
  theme(
    strip.text = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
    axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
    axis.title.y = element_text(color = "black", size = 1.4 * rel(1)),
    legend.position = "bottom",
    legend.title = element_text(color = "black", size = 1.3 * rel(1)),
    legend.text = element_text(color = "black", size = .9 * rel(1)),
    plot.title = element_text(color = "black", size = 15))

Treg_predictions

#save to pdf
# pdf(file = "/Volumes/rstor-henao_lab/Pablo/IMPAcTB-Flow-pipeline/Treg_predictions.pdf",   # The directory you want to save the file in
#     width = 10, # The width of the plot in inches
#     height = 5) # The height of the plot in inches
# print(Treg_predictions)
# dev.off()
```



# Calculate the odds ratios and plot 
```{r echo=TRUE}
CI <- exp(confint(l_mod1))
# Extract coefficients
coefficients <- summary(l_mod1)$coef

# Define a significance threshold (e.g., 0.05)
significance_threshold <- 0.05

# Filter significant coefficients
significant_coefficients <- coefficients[coefficients[, 4] < significance_threshold, ]

# Calculate odds ratios
odds_ratios <- exp(significant_coefficients[, 1])

# Add variable names for interpretation
odds_ratios <- data.frame(
  Odds_Ratio = odds_ratios)



odds_ratios <- as.data.frame(odds_ratios) %>% 
    rownames_to_column('Variable')
CI_df <- as.data.frame(CI) %>%
    rownames_to_column('Variable')


odds_ratios <- inner_join(odds_ratios, CI_df, by = "Variable")
odds_ratios$Variable <- gsub("^group", "", odds_ratios$Variable)
odds_ratios <- odds_ratios %>%
  filter(Variable != "(Intercept)")

odds_ratios
```



```{r echo=TRUE}

# Extract the CI values
variables <- odds_ratios[, 1] 
odds_ratio <- odds_ratios[, 2]
lower_ci <- odds_ratios[, 3] 
upper_ci <- odds_ratios[, 4]


odds_data <- data.frame(
  variables = variables,
  odds_ratio = odds_ratio,
  lower_ci = lower_ci,
  upper_ci = upper_ci)

odds_data$variables <- gsub("group", "", odds_data$variables)
odds_data$variables <- gsub("sex", "", odds_data$variables)
odds_data$variables <- gsub("male", "Male", odds_data$variables)
odds_data$variables <- gsub("day", "Day", odds_data$variables)
odds_data$variables <- gsub(":", " & ", odds_data$variables)

# Reorder the order of "odds_ratios"
odds_data$variables <- factor(odds_data$variables, levels = odds_data$variables[order(odds_data$odds_ratio)])

# Create a plot

Treg_significant_odds_ratios <- ggplot(odds_data, aes(x = odds_ratio, y = variables)) +
  geom_point(color = "black", size = 3) +
  geom_errorbarh(aes(xmin = lower_ci, xmax = upper_ci), height = 0, color = "black") +
  labs(title = "Odds of CD8+",
       x = "Odds Ratio",
       y = "Variable") +
  scale_x_continuous(breaks = c(0, 1, 2, 5, 10, 15)) +
  geom_text(aes(label = round(odds_ratio, 2)), vjust = -0.5, color = "black") +
  theme_minimal() +
  theme(
    strip.text = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 1.3 * rel(1)),
    axis.title.x = element_text(color = "black", size = 1.3 * rel(1)),
    axis.text.y = element_text(color = "black", size = 1.3 * rel(1)),
    axis.title.y = element_text(color = "black", size = 1.4 * rel(1)),
    legend.position = "bottom",
    legend.title = element_text(color = "black", size = 1.3 * rel(1)),
    legend.text = element_text(color = "black", size = .9 * rel(1)),
    axis.line = element_line(color = "black"),
    plot.title = element_text(color = "black", size = 15))


Treg_significant_odds_ratios




# #save to pdf
# pdf(file = "/Volumes/rstor-henao_lab/Pablo/IMPAcTB-Flow-pipeline/Treg_significant_odds_ratios.pdf",   # The directory you want to save the file in
#     width = 8, # The width of the plot in inches
#     height = 5) # The height of the plot in inches
# print(Treg_significant_odds_ratios)
# dev.off()
```


```{r}
# em_means <- emmeans(l_mod2, specs = ~ group * day + sex)
# 
# # Perform pairwise comparisons using Tukey's method
# pairwise_comparisons <- emmeans::contrast(em_means, method = "pairwise", adjust = "tukey")
# 
# pairwise_comparisons <- as.data.frame(pairwise_comparisons)
# 
# # View the results of the pairwise comparisons
# significant_comparisons <- subset(pairwise_comparisons, p.value < 0.05)
```


EXPLORATORY ANALYSIS in progress
```{r eval=FALSE, fig.height=20, fig.width=10, include=FALSE}
# 
# # Running Stats and Selecting Significant Cell Type Differences for Gated Cells TukeyHSD
# cell_stats <- tidy_Df1 %>%
#    group_by(cell_types) %>%
#   nest() %>%
#   mutate(aov_result = map(data, ~aov(percentage_of_LIVE ~ group, data = .x)),
#          tukey_result = map(aov_result, TukeyHSD),
#          tidy_tukey = map(tukey_result, broom::tidy)) %>%
#   unnest(tidy_tukey, .drop = TRUE) %>%
#   separate(contrast, into = c("contrast1", "contrast2"), sep = "-") %>%
#   dplyr::select(-data, -aov_result, -tukey_result, -term, -null.value) %>%
#   filter(adj.p.value <= 0.05)
# 
# 
# # Join Dataframes Based on Significance and Cell Types
# common_cell_types <- intersect(tidy_Df1$cell_types, cell_stats$cell_types)
# tidy_Df1_filtered <- tidy_Df1 %>%
#   filter(cell_types %in% common_cell_types)
# 
# joined_df <- left_join(tidy_Df1_filtered, cell_stats, by = "cell_types")
# 
# unique(joined_df$group)
# # Plot: Group Comparison of Activated T-cells (Combined Days)
# t_cell_activationPLOT %>%
#   mutate(group = fct_relevel(group, "Saline", "BCG", "ID93+GLA-SE", "BCG-ID93+GLA-SE")) %>%
#   ggplot(aes(x = group, y = proportion_of_activated_tcells, fill = group, color = group)) +
#   geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
#   geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
#              position = position_dodge(width = 0.75)) +
#     labs(title = "Regulatory Tcells", x = "Group", y = "% activated T-cells (normalized to CD44+)", color = "Vaccine") +
#   guides(fill = "none", shape = guide_legend(title = "Vaccine")) +
#   theme_bw() + 
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
# 
# # Plot: Group Comparison of Activated T-cells (Facet-wrapped by Day)
# t_cell_activationPLOT  %>%
#   mutate(group = fct_relevel(group, "Saline", "BCG", "ID93+GLA-SE", "BCG-ID93+GLA-SE")) %>%
#   ggplot(aes(x = group, y = proportion_of_activated_tcells, fill = group, color = group)) +
#   geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
#   geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
#              position = position_dodge(width = 0.75)) +
#     labs(title = "Regulatory Tcells by Day", x = "Group", y = "% activated T-cells (normalized to CD44+)", color = "Vaccine") +
#   guides(fill = "none", shape = guide_legend(title = "Vaccine")) +
#   theme_bw() + 
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   facet_wrap(~ day, scales = "free_y", ncol = 4, strip.position = "top")
# 
# t_cell_activationPLOT  %>%
#   mutate(group = fct_relevel(group, "Saline", "BCG", "ID93+GLA-SE", "BCG-ID93+GLA-SE")) %>%
#   ggplot(aes(x = day, y = proportion_of_activated_tcells, fill = group, color = group)) +
#   geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
#   geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
#              position = position_dodge(width = 0.75)) +
#     labs(title = "Regulatory Tcells by Day", x = "Group", y = "% activated T-cells (normalized to CD44+)", color = "Vaccine") +
#   guides(fill = "none", shape = guide_legend(title = "Vaccine")) +
#   theme_bw() + 
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
# 
# 
# # Plot: Activated T-cells by Sex (Group Comparison with t-tests)
# t_cell_activationPLOT  %>%
#   mutate(group = fct_relevel(group, "Saline", "BCG", "ID93+GLA-SE", "BCG-ID93+GLA-SE")) %>%
#   ggplot(aes(x = sex, y = proportion_of_activated_tcells, fill = sex, color = sex)) +
#   geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
#   geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
#              position = position_dodge(width = 0.75)) +
#   theme_bw() +
#    labs(title = "Regulatory Tcells by Sex", x = "Sex", y = "Regulatory Tcells by Sex and Day") + 
#   stat_compare_means(method = "t.test")
# 
# 
# # Plot: Activated T-cells by Sex and day (Facet-wrapped by Group with t-test)
# t_cell_activationPLOT  %>%
#   mutate(group = fct_relevel(group, "Saline", "BCG", "ID93+GLA-SE", "BCG-ID93+GLA-SE")) %>%
#   ggplot(aes(x = sex, y = proportion_of_activated_tcells, fill = sex, color = sex)) +
#   geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
#   geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
#              position = position_dodge(width = 0.75)) +
#   theme_bw() +
#   facet_wrap(~ day, ncol = 1) +
#   labs(title = "Regulatory Tcells by Sex and Day", x = "Sex", y = "% Activated T-cells (normalized to CD44+)")  + 
#   stat_compare_means(method = "t.test", label.y = 5)
```


Saving plots to PDF
```{r eval=FALSE, include=FALSE}
# #save to pdf
# pdf(file = "/Volumes/cvmbs/RSTOR-HenaO_lab/Pablo/SOLOVAX TB/SolovaxTB immunogenicity day 14/Unmixed/FlowJo/CD45_Final_Lung_Plots.pdf",   # The directory you want to save the file in
#    width = 25, # The width of the plot in inches
#    height = 35) # The height of the plot in inches
# plot(CD45_Final_Lung_Plots)
# dev.off()
```

